\LARGE \bf Towards a Data-driven Approach to Motion Planning

### 2014-10-01 paper2015asml.tex
local changes

\todo formulae for optimization objectives?

@@

In all, we utilized three different classification frameworks to predict overall ratings-decision trees, random forests and boosting. As a base framework we first construct a decision tree model.  Decision trees for classification provide a good visual representation especially in the presence of complex features, where the relationships between predictors and response is not immediately obvious. Figure ~\ref{fig:decision_tree} shows our base decision tree model. The features of interest in this tree include the DTW distance computed for the wrist, the hausdorf distance computed for the end-effector and the max curvature computed for the elbow. Using 10-fold cross-validation, we also design a simpler tree that has just three terminal nodes with the $wrist_tool_dtw$ feature serving as the key discriminant among the classes. This tree has an accuracy of 86\% on the test data. It is clear that the BFS path, which serves as the nominal path for computing both the DTW and Hausdorf distance, is a good approximation of the path expected by the human observer for the end-effector of the robot. It is also clear that paths where the elbow has unnecessarily large motions are also penalized by human observers.

@@

Fig.~\ref{fig:feature_importance_1} and Fig.~\ref{fig:feature_importance_2} show two measures of variable (or feature) importance. The first measure shows the mean decrease in accuracy for each feature. The importance of a feature is determined by how much the accuracy of the random forest is affected by comparing, for each tree, the OOB error with the error obtained after permuting each feature. The differences are averaged across trees and normalized.  The second measure is based on the Gini index and measures the total decrease in node heterogeneity/impurities from splitting on the feature.  For both measures higher values denote that the features are more important.

@@

>>>>

@@

In all, we utilized three different classification frameworks to predict overall ratings-decision trees, random forests and boosting. As a base framework we first construct a decision tree model.  Decision trees for classification provide a good visual representation especially in the presence of complex features, where the relationships between predictors and response is not immediately obvious. Figure ~\ref{fig:decision_tree} shows our base decision tree model. The features of interest in this tree include the DTW distance computed for the wrist (vs. the tool path), the hausdorf distance computed for the end-effector and the max curvature computed for the elbow. Using 10-fold cross-validation, we also design a simpler tree that has just three terminal nodes with the $wrist\_tool\_dtw$ feature serving as the key discriminant among the classes. This tree has an accuracy of 86\% on the test data. The $wrist\_tool\_dtw$ compares, using DTW, the path taken by the wrist vs. the path take by the tool. Large values of this feature correspond to extra rotations of the wrist as the tool is moving towards the goal - such motions are rated as low quality by the human observers.

@@

Fig.~\ref{fig:feature_importance_1} and Fig.~\ref{fig:feature_importance_2} show two measures of variable (or feature) importance. The first measure shows the mean decrease in accuracy for each feature. The importance of a feature is determined by how much the accuracy of the random forest is affected by comparing, for each tree, the OOB error with the error obtained after permuting each feature. The differences are averaged across trees and normalized.  The second measure is based on the Gini index and measures the total decrease in node heterogeneity/impurities from splitting on the feature.  For both measures higher values denote that the features are more important. Again, the $wrist\_tool\_dtw$ feature stands out as one of the more important features in building the classifer. Two path lengths $tool\_length$ (the distance traveled by the tool) and $path\_length$ (the total distance traveled in joint space) also serve as important features - in most environments the total distance traveled by the arm between start and goal locations is expected to be small. The $tool\_quat\_dist$ and $wrist\_quat\_dist$ measure the rotation of the end-effector and it seems natural that excessive rotations of the end-effector would contribute to trajectories getting a bad rating. It is also clear that the BFS path, which serves as the nominal path for computing both the DTW and Hausdorf distance, is a good approximation of the path expected by the human observer for the end-effector of the robot.

The third classification framework that we use is Boosting. In the Boosting  framework, the trees are grown sequentially, using information (weights) from previously grown trees.  The algorithm adaptively changes the distribution of the training data by iteratively reweighting each observation in each iteration.  The weights are updated using (Breiman’s) weight updating coefficient which assigns higher weights to the wrongly classified observations and lower weights to the correctly classified examples. In every iteration, the  classifier thus focuses on the most difficult examples. Using 10-fold cross validation with all the available data, we obtain a classification accuracy of 76.7\%. Fig.~\ref{fig:gini_boosting} shows the relative importance of different features using the Boosting classifier. 7 of the top 10 features on this list are also part of the top 10 features using random forests.

@@

\begin{figure}[t]
 \centering{\includegraphics[width=0.99\linewidth]{pictures/gini}}
  \caption{Gini index (higher values indicate more important features).}
\label{fig:}
\end{figure}
